---
title       : Body Mass Index (BMI) Calculator
subtitle    : A Healthcare Shiny Application To Measure Your BMI
author      : Ho Weixing
job         : Analyst
framework   : revealjs        
highlighter : highlight.js  
hitheme     : zenburn   
widgets     : [mathjax]           
mode        : selfcontained 
knit        : slidify::knit2slides
revealjs:
  theme: sky
  transition: concave
  center: "true"
---

### Body Mass Index (BMI) Calculator
##### by Weixing Ho
A Healthcare Shiny Application To Measure Your BMI


---

### What is BMI?

Based on the definition of BMI from  [Live Science](http://www.livescience.com/40507-what-is-bmi.html):

> The body mass index, or BMI, <br> is a metric used 
> to estimate the amount of body fat a person has. 

Only two measurements are involved for BMI calculation, which are height(m) and weight(kg).

To calculate your BMI using kilograms and centimeters, divide your weight by your height squared.

$$\dfrac{mass(kg)}{height (m)^2} \ $$

---

### How to calculate BMI?
Based on the data that given by user, the application will calculate the user's BMI and shows his/her BMI status.

The BMI calculation algorithm is

```{r, echo=TRUE}
Height_CM <- 168
Weight_kg <- 60
bmi <- (Weight_kg/ ((Height_CM ^2)*0.0001)) 
bmi
```

---

### BMI Status

Our application will also shows the user's BMI status based on the condition below after it calculate the user's BMI metric. 

```{r, echo=TRUE}

# if (bmi < 15.0) {print('Very severely underweight')}
# else (bmi <= 16.0) {print('Severely underweight')} 
# else (bmi <= 18.5) {print('Underweight')}
# else (bmi <= 25.0) {print('Normal')}   
# else (bmi <= 30.0) {print('Overweight') }
# else (bmi <= 35.0) {print('Obese Class I(Moderately obese)') } 
# else (bmi <= 40.0) {print('Obese Class II (Severely obese)') }  
# else {print('Obese Class III (Very severely obese)') }
```
Standard BMI Range is:<br>
-Underweight: BMI is less than 18.5<br>
-Normal weight: BMI is 18.5 to 24.99<br>
-Overweight: BMI is 25 to 29.99<br>
-Obese: BMI is 30 or more<br>

---
### Reference Documentation
<br>
Apart from that, we have included the explaination on this application functionality and some additional information on BMI from [Medical News Today Website](http://www.medicalnewstoday.com/info/obesity/what-is-bmi.php)
<br><br>
Moreover, we also added the BMI calculations formula to the users for reference purpose.

The link to Shiny Application on Rstudio Shiny's Server:-
[Health Care Application: Body Mass Index (BMI) Calculator](https://howeixing.shinyapps.io/Developing_Data_Product_Assignment_BMI_Calculator)

